---
title: "Final Regressions"
author: "Natalie Tomeh"
date: "5/11/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    highlight: "tango"
---


```{r Set Up, message = F, warning = F, echo = F}
# Loading Libraries 
library(tidyverse)
library(tidymodels)
library(Metrics)
library(gtsummary)

library(knitr)
library(kableExtra)


# Loading 

## Functions 
load("data_editing/functions.rda")

## Data 
loaded <- read_csv("data/datasets/final.csv")

# Setting not in 
`%notin%` <- negate(`%in%`)

 
# Removing Scientific Notation 
options(scipen = 999)
```

```{r Datasets, message = F, warning = F, echo = F}
all <- lens()

with_kids <- lens(with_kids = T) 

low_income <- lens(low_income = T)

low_income_with_kids <- lens(low_income = T, with_kids = T)
```


```{r echo = F, message = F, warning = F}
with_kids_3m <- with_kids %>% 
  select(t, state, pebt) %>% 
  mutate(t = t + 4) %>% 
  filter(pebt == 1) %>% 
  rbind(with_kids %>% 
  select(t, state, pebt) %>% 
  mutate(t = t + 5) %>% 
  filter(pebt == 1)) %>% 
  arrange(state, t) %>% 
  rename(pebt_3m = pebt) %>%
  left_join(with_kids, .) %>% 
  mutate(pebt_3m = ifelse(pebt_2m == 1, 1, pebt_3m),
         pebt_3m = ifelse(is.na(pebt_3m), 0, pebt_3m))


low_income_with_kids_3m <- low_income_with_kids %>% 
  select(t, state, pebt) %>% 
  mutate(t = t + 4) %>% 
  filter(pebt == 1) %>% 
  rbind(low_income_with_kids %>% 
  select(t, state, pebt) %>% 
  mutate(t = t + 5) %>% 
  filter(pebt == 1)) %>% 
  arrange(state, t) %>% 
  rename(pebt_3m = pebt) %>%
  left_join(low_income_with_kids, .) %>% 
  mutate(pebt_3m = ifelse(pebt_2m == 1, 1, pebt_3m),
         pebt_3m = ifelse(is.na(pebt_3m), 0, pebt_3m))
```




# Variable Summaries 

```{r message = F, warning = F, echo = F}

summary_tabling <- function(df){
  
  numeric_vars <- df %>% 
    select(- month, -month_num, - state, -perc_snap_m1, -t_dummy, -t, -t1, -t2, -w2, -pebt_post, -pebt_1m, -pebt_2m) 
  
  numeric_vars <- numeric_vars %>% 
    select(people, names(numeric_vars)) 
  
  map_dfr(numeric_vars, mean) %>% 
    pivot_longer(cols = 1:15, names_to = "variable", values_to = "Mean") %>% 
    left_join(map_dfr(numeric_vars, min) %>% 
                pivot_longer(cols = 1:15, names_to = "variable", values_to = "Min")) %>% 
    left_join(map_dfr(numeric_vars, max) %>% 
                pivot_longer(cols = 1:15, names_to = "variable", values_to = "Max")) %>% 
    mutate_if(is.numeric, round, digits = 2) %>% 
    mutate_if(is.numeric, format, nsmall = 2) %>%
    mutate(Mean = ifelse(variable == "people", 
                         Mean %>% 
                           as.numeric %>% 
                           comma_format()() %>% 
                           format(nsmall = 0) %>% 
                           str_remove("\\..*"), 
                         Mean),
           Min = ifelse(variable == "people", 
                         Min %>% 
                           as.numeric %>% 
                           comma_format()() %>% 
                           format(nsmall = 0) %>% 
                           str_remove("\\..*"), 
                         Min),
           Max = ifelse(variable == "people", 
                        Max %>% 
                           as.numeric %>% 
                           comma_format()() %>% 
                           format(nsmall = 0) %>% 
                           str_remove("\\..*"), 
                         Max),
           ) %>% 
    mutate(Range = paste(Min, " - ", Max)) %>% 
    select(variable, Mean, Range) 

}


summary_df <- summary_tabling(all) %>% 
  rename("Meanx" = "Mean", "Rangex" = "Range") %>% 
  left_join(summary_tabling(with_kids)) %>% 
  rename("Meany" = "Mean", "Rangey" = "Range") %>% 
  left_join(summary_tabling(low_income))

names(summary_df) <- c(" ", "Mean", "Range", "Mean", "Range", "Mean", "Range")


summary_df %>% 
  kable() %>% 
  kable_classic(html_font = "Times") %>% 
  pack_rows(index = c("Population" = 1, "Program Participation" = 2, 
            "Outcome Variables" = 3, "Education" = 4, "Race/Ethnicity" = 5)) %>% 
  add_header_above(c(" " = 1, "All Households" = 2, "Households With Kids" = 2, "Low Income Households" = 2))

  
```

# Naive Regressions 

```{r message = F, warning = F, echo = F, eval = F }
## Note: eval = False because this is an old version of the naive regressions 

# All With Children - Food Insecurity 
pebt_fi <- lm(perc_fi ~ pebt, weights = people, data = with_kids)
snap_fi <- lm(perc_fi ~ perc_snap, weights = people, data = with_kids)
both_fi <- lm(perc_fi ~ pebt + perc_snap, weights = people, data = with_kids)

# All With Children - Hunger 
pebt_hungry <- lm(perc_hungry ~ pebt, weights = people, data = with_kids)
snap_hungry <- lm(perc_hungry ~ perc_snap, weights = people, data = with_kids)
both_hungry <- lm(perc_hungry ~ pebt + perc_snap, weights = people, data = with_kids)

# All With Children - NonConfident 
pebt_nonconf <- lm(perc_nonconf ~ pebt, weights = people, data = with_kids)
snap_nonconf <- lm(perc_nonconf ~ perc_snap, weights = people, data = with_kids)
both_nonconf <- lm(perc_nonconf ~ pebt + perc_snap, weights = people, data = with_kids)

making_nice(
  list(pebt_fi, snap_fi, both_fi, pebt_hungry, snap_hungry, both_hungry, pebt_nonconf, snap_nonconf, both_nonconf),
  c("a", "b", "c", "d", "e", "f", "g", "h", "i"),
  override_names = T,
  c(" " = 1, "P-EBT" = 1, "SNAP" = 1, "P-EBT and SNAP" = 1,
    "P-EBT" = 1, "SNAP" = 1, "P-EBT and SNAP" = 1,
    "P-EBT" = 1, "SNAP" = 1, "P-EBT and SNAP" = 1),
  c(" " = 1, "Food Insecurity" = 3, "Hunger" = 3, "Food Non-Confidence" = 3),
  naive = T
)
```


#### Food Insecurity   

Households With Children 

```{r message = F, warning = F, echo = F}
# Food Insecurity 
# All With Children - Food Insecurity 
snap_fi <- lm(perc_fi ~ perc_snap, weights = people, data = with_kids)

pebt_fi <- lm(perc_fi ~ pebt, weights = people, data = with_kids)
both_fi <- lm(perc_fi ~ pebt + perc_snap, weights = people, data = with_kids)

pebt_post_fi <- lm(perc_fi ~ pebt_post, weights = people, data = with_kids)
both_post_fi <- lm(perc_fi ~ pebt_post + perc_snap, weights = people, data = with_kids)

pebt_1m_fi <- lm(perc_fi ~ pebt_1m, weights = people, data = with_kids)
both_1m_fi <- lm(perc_fi ~ pebt_1m + perc_snap, weights = people, data = with_kids)


pebt_2m_fi <- lm(perc_fi ~ pebt_2m, weights = people, data = with_kids)
both_2m_fi <- lm(perc_fi ~ pebt_2m + perc_snap, weights = people, data = with_kids)

making_nice(
  list(snap_fi, pebt_fi, both_fi, pebt_post_fi, both_post_fi, pebt_1m_fi, both_1m_fi, pebt_2m_fi, both_2m_fi), 
  c("a", "b", "c", "d", "e", "f", "g", "h", "i"), 
   override_names = T, 
  c(" " = 1, "SNAP"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1,"P-EBT"= 1, "Both"= 1),
  c(" " = 2, "Release Week" = 2, "Lagged" = 2, "1 Month" = 2, "2 Month" = 2),
  naive = T
) 

```

#### Hunger

Households With Children 

```{r message = F, warning = F, echo = F}
# Food Insecurity 
# All With Children - Food Insecurity 
snap_hungry <- lm(perc_hungry ~ perc_snap, weights = people, data = with_kids)

pebt_hungry <- lm(perc_hungry ~ pebt, weights = people, data = with_kids)
both_hungry <- lm(perc_hungry ~ pebt + perc_snap, weights = people, data = with_kids)

pebt_post_hungry <- lm(perc_hungry ~ pebt_post, weights = people, data = with_kids)
both_post_hungry <- lm(perc_hungry ~ pebt_post + perc_snap, weights = people, data = with_kids)

pebt_1m_hungry <- lm(perc_hungry ~ pebt_1m, weights = people, data = with_kids)
both_1m_hungry <- lm(perc_hungry ~ pebt_1m + perc_snap, weights = people, data = with_kids)


pebt_2m_hungry <- lm(perc_hungry ~ pebt_2m, weights = people, data = with_kids)
both_2m_hungry <- lm(perc_hungry ~ pebt_2m + perc_snap, weights = people, data = with_kids)

pebt_3m_hungry <- lm(perc_hungry ~ pebt_2m, weights = people, data = with_kids)
both_3m_hungry <- lm(perc_hungry ~ pebt_2m + perc_snap, weights = people, data = with_kids)


making_nice(
  list(snap_hungry, pebt_hungry, both_hungry, pebt_post_hungry, both_post_hungry, pebt_1m_hungry, both_1m_hungry, pebt_2m_hungry, both_2m_hungry), 
  c("a", "b", "c", "d", "e", "f", "g", "h", "i"), 
   override_names = T, 
  c(" " = 1, "SNAP"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1),
  c(" " = 2, "Release Week" = 2, "Lagged" = 2, "1 Month" = 2, "2 Month" = 2),
  naive = T
) 
```


#### Food Non-Confidence 

Households With Children 


```{r message = F, warning = F, echo = F}
# Food Insecurity 
# All With Children - Food Insecurity 
snap_nonconf <- lm(perc_nonconf ~ perc_snap, weights = people, data = with_kids)

pebt_nonconf <- lm(perc_nonconf ~ pebt, weights = people, data = with_kids)
both_nonconf <- lm(perc_nonconf ~ pebt + perc_snap, weights = people, data = with_kids)

pebt_post_nonconf <- lm(perc_nonconf ~ pebt_post, weights = people, data = with_kids)
both_post_nonconf <- lm(perc_nonconf ~ pebt_post + perc_snap, weights = people, data = with_kids)

pebt_1m_nonconf <- lm(perc_nonconf ~ pebt_1m, weights = people, data = with_kids)
both_1m_nonconf <- lm(perc_nonconf ~ pebt_1m + perc_snap, weights = people, data = with_kids)


pebt_2m_nonconf <- lm(perc_nonconf ~ pebt_2m, weights = people, data = with_kids)
both_2m_nonconf <- lm(perc_nonconf ~ pebt_2m + perc_snap, weights = people, data = with_kids)


making_nice(
  list(snap_nonconf, pebt_nonconf, both_nonconf, pebt_post_nonconf, both_post_nonconf, pebt_1m_nonconf, both_1m_nonconf, pebt_2m_nonconf, both_2m_nonconf), 
  c("a", "b", "c", "d", "e", "f", "g", "h", "i"), 
   override_names = T, 
  c(" " = 1, "SNAP"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1, "P-EBT"= 1, "Both"= 1),
  c(" " = 2, "Release Week" = 2, "Lagged" = 2, "1 Month" = 2, "2 Month" = 2),
  naive = T
) 
```




# SNAP Alone

## All Households 

```{r echo = F, message = F, warning = F}

safi <- lm(perc_fi ~ perc_snap + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = all)

sah <- lm(perc_hungry ~ perc_snap + t1 + t2 + state +  w2 + 
            perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = all)


sanc <- lm(perc_nonconf ~ perc_snap + t1 + t2 + state +  w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = all)

making_nice(
  list(safi, sah, sanc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence")
)

```

## Households With Kids and Low Income Households 

```{r echo = F, message = F, warning = F}
## Households With Kids 

skfi <- lm(perc_fi ~ perc_snap + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

skh <- lm(perc_hungry ~ perc_snap + t1 + t2 + state +  w2 + 
            perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

sknc <- lm(perc_nonconf ~ perc_snap + t1 + t2 + state +  w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)


## Low Income Households 
slifi <- lm(perc_fi ~ perc_snap + t1 + t2 + state +  w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income)

slih <- lm(perc_hungry ~ perc_snap + t1 + t2 + state +  w2 + 
            perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income)

slinc <- lm(perc_nonconf ~ perc_snap + t1 + t2 + state +  w2 + 
            perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income)


# Table 

making_nice(
  list(skfi, skh,sknc, slifi, slih, slinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households" = 3)
)
```



# P-EBT - Across Various Treatment Horizons 

## P-EBT Treatment Horizon: Period of Release (two weeks)

#### P-EBT Alone 

```{r echo = F, message = F, warning = F}

## Households With Kids 

pkfi <- lm(perc_fi ~ pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

pkh <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

pknc <- lm(perc_nonconf ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

## Low Income Households 

plifi <- lm(perc_fi ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids)

plih <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids)

plinc <- lm(perc_nonconf ~ pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids)
# Table
making_nice(
  list(pkfi, pkh, pknc, plifi, plih, plinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```

##### P-EBT and SNAP 

```{r echo = F, message = F, warning = F}

## Households With Kids 

bkfi <- lm(perc_fi ~ pebt + t1 + t2 + state + w2 +  perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

bkh <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

bknc <- lm(perc_nonconf ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids)

## Low Income Households 

blifi <- lm(perc_fi ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids)

blih <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids)

blinc <- lm(perc_nonconf ~ pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids)
# Table
making_nice(
  list(bkfi, bkh, bknc, blifi, blih, blinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)

```


## P-EBT Treatment Horizon: Period After Release (two weeks)

#### P-EBT Alone 

```{r echo = F, message = F, warning = F}

## Households With Kids 

pkfi <- lm(perc_fi ~ pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("week after"))

pkh <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("week after"))

pknc <- lm(perc_nonconf ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("week after"))

## Low Income Households 

plifi <- lm(perc_fi ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("week after"))

plih <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("week after"))

plinc <- lm(perc_nonconf ~ pebt + t1 + t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("week after"))
# Table
making_nice(
  list(pkfi, pkh, pknc, plifi, plih, plinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```

##### P-EBT and SNAP 

```{r echo = F, message = F, warning = F}

## Households With Kids 

bkfi <- lm(perc_fi ~ pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("week after"))

bkh <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("week after"))

bknc <- lm(perc_nonconf ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("week after"))

## Low Income Households 

blifi <- lm(perc_fi ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("week after"))

blih <- lm(perc_hungry ~  pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("week after"))

blinc <- lm(perc_nonconf ~ pebt + t1 + t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("week after"))
# Table
making_nice(
  list(bkfi, bkh, bknc, blifi, blih, blinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```


## P-EBT Treatment Horizon: Period of Release + Period After Release (one month)

#### P-EBT Alone 

```{r echo = F, message = F, warning = F}

## Households With Kids 

pkfi <- lm(perc_fi ~ pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("one month"))

pkh <- lm(perc_hungry ~  pebt*t1 + pebt*t2+ state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("one month"))

pknc <- lm(perc_nonconf ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("one month"))

## Low Income Households 

plifi <- lm(perc_fi ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("one month"))

plih <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("one month"))

plinc <- lm(perc_nonconf ~ pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("one month"))
# Table
making_nice(
  list(pkfi, pkh, pknc, plifi, plih, plinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```

##### P-EBT and SNAP 

```{r echo = F, message = F, warning = F}

## Households With Kids 

bkfi <- lm(perc_fi ~ pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("one month"))

bkh <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("one month"))

bknc <- lm(perc_nonconf ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("one month"))

## Low Income Households 

blifi <- lm(perc_fi ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("one month"))

blih <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("one month"))

blinc <- lm(perc_nonconf ~ pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("one month"))
# Table
making_nice(
  list(bkfi, bkh, bknc, blifi, blih, blinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```


## P-EBT Treatment Horizon: Period of Release - Two Periods After Release (two months)

#### P-EBT Alone 

```{r echo = F, message = F, warning = F}

## Households With Kids 

pkfi <- lm(perc_fi ~ pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("two months"))

pkh <- lm(perc_hungry ~  pebt*t1 + pebt*t2+ state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("two months"))

pknc <- lm(perc_nonconf ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("two months"))

## Low Income Households 

plifi <- lm(perc_fi ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("two months"))

plih <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("two months"))

plinc <- lm(perc_nonconf ~ pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("two months"))
# Table
making_nice(
  list(pkfi, pkh, pknc, plifi, plih, plinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```

##### P-EBT and SNAP 

```{r echo = F, message = F, warning = F}

## Households With Kids 

bkfi <- lm(perc_fi ~ pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("two months"))

bkh <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("two months"))

bknc <- lm(perc_nonconf ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids %>% change_pebt("two months"))

## Low Income Households 

blifi <- lm(perc_fi ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("two months"))

blih <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("two months"))

blinc <- lm(perc_nonconf ~ pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids %>% change_pebt("two months"))
# Table
making_nice(
  list(bkfi, bkh, bknc, blifi, blih, blinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```





## P-EBT Treatment Horizon: Three Months After Release


#### P-EBT Alone 

```{r echo = F, message = F, warning = F}

## Households With Kids 

pkfi <- lm(perc_fi ~ pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids_3m)

pkh <- lm(perc_hungry ~  pebt*t1 + pebt*t2+ state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids_3m)

pknc <- lm(perc_nonconf ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids_3m)

## Low Income Households 

plifi <- lm(perc_fi ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids_3m)

plih <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids_3m)

plinc <- lm(perc_nonconf ~ pebt*t1 + pebt*t2 + state + w2 + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids_3m)
# Table
making_nice(
  list(pkfi, pkh, pknc, plifi, plih, plinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```

##### P-EBT and SNAP 

```{r echo = F, message = F, warning = F}

## Households With Kids 

bkfi <- lm(perc_fi ~ pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids_3m)

bkh <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids_3m)

bknc <- lm(perc_nonconf ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = with_kids_3m)

## Low Income Households 

blifi <- lm(perc_fi ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids_3m)

blih <- lm(perc_hungry ~  pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids_3m)

blinc <- lm(perc_nonconf ~ pebt*t1 + pebt*t2 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = low_income_with_kids_3m)
# Table
making_nice(
  list(bkfi, bkh, bknc, blifi, blih, blinc), 
  c("Food Insecurity", "Hunger", "Food Non-Confidence", 
    "Food Insecurity ", "Hunger ", "Food Non-Confidence "),  
 header_row_titles = c(" " = 1, "Households With Children" = 3, "Low Income Households With Children" = 3)
)
```



```{r}
a <- low_income_with_kids %>% 
  mutate(t2 = ifelse(t2 > 4, 0 , t2),
         t3 = ifelse(t > 12, t - 12, 0)) %>% 
  lm(perc_nonconf ~ pebt_1m*t1 + pebt_1m*t2 + pebt_1m*t3 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = .)

b <- low_income_with_kids %>% 
  mutate(t2 = ifelse(t2 > 4, 0 , t2),
         t3 = ifelse(t > 12, t - 12, 0)) %>% 
  lm(perc_fi ~ pebt_1m*t1 + pebt_1m*t2 + pebt_1m*t3 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = .)

c <- low_income_with_kids %>% 
  mutate(t2 = ifelse(t2 > 4, 0 , t2),
         t3 = ifelse(t > 12, t - 12, 0)) %>% 
  lm(perc_hungry ~ pebt_1m*t1 + pebt_1m*t2 + pebt_1m*t3 + state + w2 + perc_snap + 
             perc_asian + perc_black + perc_latino + perc_other + 
             perc_some_college + perc_highschool + perc_no_highschool,
            weights = people, 
            data = .)


summary(c)
```



